A Massive Molecular Gas Reservoir in the $z$ = 2.221 Type-2 Active Galactic Nucleus Host Galaxy SMM J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-07-04 skeleton.tex
Done Radio SED section for now

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}
Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing frequencies, 
and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the 
spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. At observed-frame $\sim$90 GHz, 
observations of the FR-II radio galaxy, 3C220.1 at $z$ = 0.610 has been reported to be the case 
\citep{Hardcastle08a}. Besides, an upper 
limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) appears to 
be indicative of a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
Consequently, we would naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$ = 7.18 $\pm$ 0.69 mJy to be dominated by the unresolved core component of the foreground FR-II, which is at $z$ = 0.685. == wouldn't this be contradicting if we know the core is unresolved, why would we jump into looking at the integrated flux ==
However, the inferred deconvolved spatial size of the source matching that in a resolved image (in Figure 1) is 
suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to 
existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
estimate the flux density of the lobes at the frequency of our continuum measurement. 
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobes can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution. 
The extrapolated flux density of the lobe-fit at 104 GHz is consistent with the peak flux density of our continuum measurement (Figure \ref{fig:SED}). The 10$\sigma$ detection of the continuum thereby suggests
a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward the core. Moreover, the peak position of the 104 GHz continuum is
centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. 
%This finding 
%is consistent with a recent study by \citet{Hardcastle08a}, where they reported null detection of the radio cores of 
%two FR-II radio galaxies 3C 20 at $z$ = 0.174 and 3C 295 at $z$ = 0.461 at observed-frame $\sim$90GHz. 
We do not extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are taken 
across epochs.

Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, while others exhibit a clear spectral steepening either between cm and mm wavelengths (e.g., 3C123); at the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes. But it would be important for hotpot emission studies because this is at restframe sim60 GHz,

>>>>

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}
Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing frequencies, 
and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the 
spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. At observed-frame $\sim$ 90 GHz, 
observations of the FR-II radio galaxy, 3C220.1 at $z$ = 0.610 has been reported to be the case 
\citep{Hardcastle08a}. Besides, an upper 
limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and a clear detection of 0.8 mJy at 9 GHz (H14) appears to 
be indicative of a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
Consequently, we would naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$ = 7.18 $\pm$ 0.69 mJy to be dominated by the unresolved core component of the foreground FR-II, which is at $z$ = 0.685. == wouldn't this be contradicting if we know the core is unresolved, why would we jump into looking at the integrated flux ==
However, the inferred deconvolved spatial size of the source matching that in a resolved image (in Figure 1) is 
suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to 
existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
estimate the flux density of the lobes at the frequency of our continuum measurement. 
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobes emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending 
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches 
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy 
distribution. 
The extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum 
measurement (Figure \ref{fig:SED}). The 10$\sigma$ detection of the continuum thereby suggests
a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward 
the core. Moreover, the peak position of the 104 GHz continuum is
centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. We did not 
extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
taken 
across epochs.\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, and some exhibit spectral steepening either between cm or mm wavelengths (e.g., 3C123); at the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes. Nonetheless, high resolution observations of 3C220.3 at mm wavelengths (rest-frame $\sim$ 60 GHz) will provide important insight on hotspot emission studies.
